---
title: "Ex 3: Intro to Survival Analysis"
author: "Raegan Gutierrez"
date: "2023-02-26"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(survminer)
library(survival)
```

## Question 1

**You are studying three different new drugs that may help slow the progression of Alzheimer’s.  Do the following:**

*a.	Draw a survival plot that shows the survival curves for all three drugs.*

*b.	Test to see if overall there is an effect of any of the drugs on survival taken as a global set.*

*c.	Compare the survival curves for each of the three drugs with each other (three comparisons) and see if any if the curves are different from each other.  *



```{r}
#Read in data 
df2 = read.csv("alzheimers data.csv")
```

```{r}
#part a: Survival Curve
fit2 <- survfit(Surv(Time, Event)~Group, data = df2)

ggsurvplot(fit2, df2)

```

```{r}
#part b: LogRank test
survdiff(Surv(Time, Event)~Group, data=df2)
```

The Log Rank test returned a p-value less than 0.05, meaning there is a significant difference between the groups. At least one of the drugs is different compared to the other two. 

```{r}
#part c: Pairwise LogRank test
pairwise_survdiff(Surv(Time, Event)~Group, data=df2)
```

The difference between groups 1 and 2 is significant, and the difference between groups 2 and 3 is significant. There is no significant difference between group 1 and group 3. Based off of these results and our survival curve, we can conclude that the drug used in treatment group 2 is significantly better at slowing the progression of Alzheimer’s compared to the other two drugs used in groups 1 and 3. 
